---
title: "Functions and examples for hypothetical gym"
author: Matthew Newbold
output: html_document
---
# Tenative Functions

This document contains, as requested by the assignment, a series of functions 
for R programing in relation to the final project that has been assigned for 
the course. 
The idea behind the functions is that the functions will be able to be fed a 
dataset purporting to represent a fictional gym and the daily uses of various 
resources in the gym over the course of a year for a five year period. The first
function should allow for the generation of a yearly mean, with the second 
hopefully allowing for a mean of all the years for a service at once. The final 
function that I have currently written would hopefully allow me to take the 
means for each year for each topic/data and then convert them into per-year 
graphs, allowing for the data to be visually presented.   

# Non-visual functions  

## Various Services Use per Day by Quarter by Year    
Note that, in order to have any given function listed here focus on a given 
column (and DailyUsePerYearMean requires that you do), you need to specify when writing the inserted dataset, usually by adding 
[,x] to the end, where x is the column you need to access. 
```{r}
DailyUsePerYearMean<-function(x){
  x2030<-mean(x[1:4])
  x2031<-mean(x[5:8])
  x2032<-mean(x[9:12])
  x2033<-mean(x[13:16])
  x2034<-mean(x[17:20])
  XDailyYearlyMeans<-cbind(x2030, x2031, x2032, x2033, x2034)
  print(XDailyYearlyMeans)
}
```

#example
DailyUsePerYearMean(HypoGymDailyAveragesByQuarter[,1])
 
## Generating Means for all columns 
```{r}
TheMeanColumnTotal<-function(x){
  TheMeanColumnTotal<-colMeans(x)
}
```  

# Visualization Tools  

## Bar Graph of Service Means by Year  
```{r}
DailyUsesChart<-function(x){
  M1<-DailyUsePerYearMean(x[,1])
  M2<-DailyUsePerYearMean(x[,2])
  M3<-DailyUsePerYearMean(x[,3])
  M4<-DailyUsePerYearMean(x[,4])
  M5<-DailyUsePerYearMean(x[,5])
  M6<-DailyUsePerYearMean(x[,6])
  barplot(M1, col = "black", main= "Member Sign-In Terminal Daily Use: Yearly Mean", xlab="Years")
  barplot(M2, col = "darkgreen", main= "Daily Use of Bodybuilding Equipment: Yearly Mean", xlab="Years")
  barplot(M3, col = "darkorchid1", main= "Daily Personal Trainer Appointments: Yearly Mean", xlab="Years")
  barplot(M4, col = "firebrick1", main= "Daily Attendence of Children's Fitness class: Yearly Mean", xlab="Years")
  barplot(M5, col = "gold", main= "Daily Use of Aerobics Equipment: Yearly Mean", xlab="Years")
  barplot(M6, col = "hotpink", main= "Daily Use of Sign-In sheet for pool: Yearly Mean", xlab="Years")
}
```  

## Line Graph of Service Means by Year
Note that par allows one to edit the grid by which the chosen graphs are 
assigned; the current grid has been chosen to establish maximum viewing comfort,
but other adjustments might be neccesary based on user needs.

```{r}
HypoGYmSereisplot21<-function(x){
    par(mfrow=c(2,3))
    plot.ts(HypoGymDailyAveragesByQuarter[,1], col= "black", lwd= 2, main="Daily     Sign In Terminal Use", ylab= "Daily Average by quarter")
    plot.ts(HypoGymDailyAveragesByQuarter[,2], col= "darkgreen", lwd= 2,    main="Daily Use of Bodybuilding Equipment", ylab= "Daily Average by quarter")
    plot.ts(HypoGymDailyAveragesByQuarter[,3], col= "darkorchid1", lwd= 2,  main="Daily Personal Trainer Appointments", ylab= "Daily Average by quarter")
    plot.ts(HypoGymDailyAveragesByQuarter[,4], col= "firebrick1", lwd= 2,       main="Daily Attendence of Children's Fitness Class", ylab= "Daily Average by  quarter")
    plot.ts(HypoGymDailyAveragesByQuarter[,5], col= "gold", lwd= 2, main="Daily     Use of Aerobics Equipment", ylab= "Daily Average by quarter")
    plot.ts(HypoGymDailyAveragesByQuarter[,6], col= "hotpink", lwd= 2,       main="Daily use of Sign In Sheet for Pool", ylab= "Daily Average by quarter")
}
```

##Histograms of Service Means by Year
```{r}
hypogymboxplot<-function(x){
    M1<-DailyUsePerYearMean(x[,1])
    M2<-DailyUsePerYearMean(x[,2])
    M3<-DailyUsePerYearMean(x[,3])
    M4<-DailyUsePerYearMean(x[,4])
    M5<-DailyUsePerYearMean(x[,5])
    M6<-DailyUsePerYearMean(x[,6])
    boxplot(M1, main= "Member Sign-In Terminal Daily Use: Yearly Mean", xlab="Years")
    boxplot(M2, main= "Daily Use of Bodybuilding Equipment: Yearly Mean", xlab="Years")
    boxplot(M3, main= "Daily Personal Trainer Appointments: Yearly Mean", xlab="Years")
    boxplot(M4, main= "Daily Attendence of Children's Fitness class: Yearly Mean", xlab="Years")
    boxplot(M5, main= "Daily Use of Aerobics Equipment: Yearly Mean", xlab="Years")
    boxplot(M6, main= "Daily Use of Sign-In sheet for pool: Yearly Mean", xlab="Years")
}
```

